### 2015-05-13 evaluation.tex
update in evaluation text

Using the race freedom guarantees that \whoop provides, we managed to significantly accelerate \corral in most of our benchmarks; the best performance was achieved using the \yieldmr instrumentation (see Table~\ref{tab:results}). Figure~\ref{fig:plot} shows that most of our speedups using \yieldmr are in the range of 1.5--10$\times$; whereas in two drivers, ssu100 and pc8736x\_gpio, we achieved $>$10$\times$ and $>$20$\times$ speedups, respectively (with csb of 9). We notice that a higher csb can result into greater speedups, when exploiting \whoop. This is expected, as a higher csb directly translates into a larger sequentialized program.

>>>>

Using the race freedom guarantees that \whoop provides, we managed to significantly accelerate \corral in most of our benchmarks; the best performance was achieved using the \yieldmr instrumentation (see Table~\ref{tab:results}). Figure~\ref{fig:plot} shows that most of our speedups using \yieldmr are in the range of 1.5--10$\times$; whereas in ssu100, and pc8736x\_gpio respectively, we achieved a speedup greater than 10$\times$, and 20$\times$ respectively, using a csb of 9. We notice that a higher csb can potentially result into greater speedups, when exploiting \whoop. This is expected, as a higher csb directly translates into a larger sequentialized program, and thus \whoop has more opportunities to reduce the sequentialization.
